plackett_luce_monster

### 2022-07-09 inst/plackett_luce_monster.Rmd
further work on university ranking

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("partitions")
```

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("partitions")
library("pdftools")
```

@@

%

@@

# University ranking analysis

Here we use a dataset of university rankings, `timesData.csv`, taken
from
`https://github.com/arnaudbenard/university-ranking/blob/master/timesData.csv`.

```{r}
a <- read.table("timesData.csv",sep=",", header=TRUE)
wanted <- c("California Institute of Technology", "Harvard University", 
"Massachusetts Institute of Technology", "Princeton University", 
"Stanford University", "University of Cambridge", "University of Oxford")
names(wanted) <- c("cal","harv","mass","prin","stan","cam","ox")

a <- a[a$university_name %in% wanted,]
a <- cbind(a,"top7rank"=0)
for(y in unique(a$year)){
    a[a$year==y,"top7rank"] <- order(
     			  as.numeric(a[a$year==y,"world_rank"]) + 
                                     a[a$year==y,"research"]/1e6,
decreasing=TRUE)}
a <- a[,c("top7rank","university_name","year")]
a <- reshape(a,idvar="university_name",timevar="year",direction="wide")
for(i in seq_len(nrow(a))){
   a$university_name[i] <- names(which(wanted == a$university_name[i]))
}
rownames(a) <- a$university_name
a <- a[,-1]
colnames(a) <- paste("Y",2011:2016,sep="")
a
H <- ordertable2supp(a)
```

```{r,label=testuniv,cache=TRUE}
equalp.test(H)
samep.test(H,c("ox","cam"))
```

Start to use `hyper3` idiom:

```{r}
H3 <- hyper3()
for(i in seq_len(ncol(a))){
  jj <- rep("",nrow(a))
  jj[a[,i]] <- rownames(a)
  print(jj)
}
```
